Equation-of-state insensitive relations after GW170817

### 2019-02-26 paper/bin-love-after-gw170817.tex
Fixed Carl's affiliation

\author{Katerina Chatziioannou}
%\affiliation{%
% Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
%}%
\affiliation{%
 Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
}%

\author{Carl-Johan Haster}
\affiliation{%
 Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
}%
\affiliation{%
 Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
}%

\author{Nicol\'as Yunes}
\affiliation{%
eXtreme Gravity Institute, Department of Physics, Montana State University, Bozeman, MT 59717, USA.
}%
\affiliation{%
 Department of Physics and MIT Kavli Institute,
}%

>>>>

\author{Katerina Chatziioannou}
%\affiliation{%
% Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
%}%
\affiliation{%
 Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, USA
}%

\author{Carl-Johan Haster}
\affiliation{%
 LIGO Laboratory and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, Massachusetts 02139, USA
}%
\author{Nicol\'as Yunes}
\affiliation{%
eXtreme Gravity Institute, Department of Physics, Montana State University, Bozeman, MT 59717, USA.
}%
\affiliation{%
 Department of Physics and MIT Kavli Institute,
}%
